---
title: "Weight of Fish"
author: "Kelly Patrizio"
date: "October 28, 2020"
output: 
  html_document:
    number_sections: true
    toc: true
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
```

```{r}
Fishdata=read.csv("Fish.csv", header = TRUE)
```


# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->

## Build the best regression model you can that predicts the weight of perch
## Using only two predictor variables 


# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

we are using num~num because the variables we are looking at are all numerical explanatory variables.

#Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results for Perch

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->


```{r}
Fishies=filter(Fishdata, Species =="Perch")
Fishies=select(Fishies,-Species)
pairs(Fishies)
``` 
The best plot for the  linear model of species "Perch" according to the above chart appears to be Length 2

### Numerical Descriptive Results for Perch

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->


```{r}
summary(Fishies)
```



```{r}
Perchmodel=lm(Weight~Length2+Width,data=Fishies)
summary(Perchmodel)
```

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Fishies,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out, statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

In the above numerical graphs for Perch the summary chart appears to show the 
Max. weight of 1100.0 oz   Max. Length of 44.00 for the lm for length2, a
Max. Height of 12.800 in. and a Max. width of 8.142 in

The perch model shows an adj r-squared prediction of 0.9341 which is pretty close
to our highest regression.

In the above subset model it appears that subset size 2 @ 0.9400 adjr2 
calculates that Height and width give the best  predictor of models.


## Inferential Results for Perch

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfies the assumptions and is appropriate to answer the research question!-->

  
```{r}
model.1 <- lm(Weight~Length2+Width,data=Fishies)
summary.lm(model.1)
```

The inferential test above agrees with the adjr2 prediction of 0.9341

## Build the best regression model you can that predicts the weight of Bream
## Using only two predictor variables 


### Graphical Descriptive Results for Bream

```{r}
FishiesB=filter(Fishdata, Species =="Bream")
FishiesB=select(FishiesB,-Species)
pairs(FishiesB)
```

In the above Graphical descriptive result chart for "Bream" it appears that 
length 1 would give us the best model for prediction.


### Numerical Descriptive Results for Bream

```{r}
summary(FishiesB)
```

In the above summary we have a max. weight of 1000 oz with a max length of 
38 in. using the Length1 variable and a max Height of 18.96 in. and a max
width of 6.8 in.

```{r}
Breammodel2=lm(Weight~Length1+ Width,data=FishiesB)
summary(Breammodel2)
```

In the Bream model 2 above we see an adjr2 of 0.9084 which is a bit lower than 
the Perch at 0.9431.


```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = FishiesB,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

In the subset chart above we can see at a subset size of 2 variables that 
Length2 and Height would be the best model to predict the results.  
It appears we have an adjr2 score of 0.934 with a multiple rsquare of 0.9137. 


## Inferential Results for Bream

  
```{r}
model.2 <- lm(Weight~Length1+Width,data=FishiesB)
summary.lm(model.2)
```

The inferential chart above appears to have an adjr2 prediction of 0.9084 still 
showing that the "Perch" is the best predicted model of the two species.  

## Build the best regression model you can that predicts the weight of Smelt
## Using only two predictor variables 


### Graphical Descriptive Results for Smelt

```{r}
FishiesS=filter(Fishdata, Species =="Smelt")
FishiesS=select(FishiesS,-Species)
pairs(FishiesS)
```

In the above graphical descriptive results chart for "Smelt", it appears that
Length3 would be the best lm to make a prediction.

### Numerical Descriptive Results for Smelt

```{r}
summary(FishiesS)
```

In the above summary chart for species "Smelt", it would appear that the
max weight for Smelt is 19.9 oz with a max length of 16.2 in. according to the 
Length3 lm.  and a max Height of 2.9 in. and a max Width of 2.1 in.


```{r}
Smeltmodel3=lm(Weight~Length3+ Width,data=FishiesS)
summary(Smeltmodel3)
```

The model3 above for Smelt appears to have an adjr2 of  0.95551
which is higher than our first prediction model of 0.9341; possibly
being the best model for prediction altogether.


```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = FishiesS,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

when we observe the subset chart it appears that the subset size of 2 
variables, shows that Length2 and Width are the best two variables to make a 
prediction at an adjr2 of 0.9551

## Inferential Results for Smelt
  
```{r}
model.3 <- lm(Weight~Length3+Width,data=FishiesS)
summary.lm(model.3)
```

The inferntial chart above for Smelt appears to also have an adjr2 of 0.9551.

# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variables causes the other, or whether they perhaps are related for some other reason.  Watch the chapter 6 videos from the George Town videos collection.!-->
