---
title: "Weight of Fish"
author: "Kelly Patrizio"
date: "October 28, 2020"
output: 
  html_document:
    number_sections: true
    toc: true
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
```

```{r}
Fishdata=read.csv("Fish.csv", header = TRUE)
```


# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->

## Build the best regression model you can that predicts the weight of perch
## Using only two predictor variables 


# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

we are using num~num because the variables we are looking at, are all numerical
explanatory variables.

#Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results for Perch

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->


```{r}
Fishies=filter(Fishdata, Species =="Perch")
Fishies=select(Fishies,-Species)
pairs(Fishies)
``` 
The best plot for the  linear model of species "Perch" according to the above 
chart appears to be Height.

### Numerical Descriptive Results for Perch

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
summary(Fishies)
```

In the above numerical graphs for Perch the summary chart appears to show the 
Max. weight of 1100.0 oz   Max. Length of 44.00 for the lm for length2, a
Max. Height of 12.800 in. and a Max. width of 8.142 in


```{r}
Perchmodel=lm(Weight~Length2+Width,data=Fishies)
summary(Perchmodel)
```


The perch linear model shows an adj r-squared prediction of 0.9341 which is pretty
close to our highest regression.

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Fishies,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out, statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

In the above leaps model it appears that the subset size of 2 variables gives us 
a statistical, adjr2 of 0.9400.  It indicates that the Height and width are
the best two variables for the models to predict the weight of the "Perch". 
This is the best subset regression for "Perch"


## Inferential Results for Perch

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfies the assumptions and is appropriate to answer the research question!-->

  
```{r}
model.1 <- lm(Weight~Length2+Width,data=Fishies)
summary.lm(model.1)
```

The inferential test above agrees with the adjr2 prediction of 0.9341 adjr2, 
using the variables...Height and width.  Therefore, it would appear that the 
subset chart using only variables height and width having an adj score 0f 
0.9400 would be the best model to make the best prediction of weight for "Perch"

## Build the best regression model you can that predicts the weight of Bream
## Using only two predictor variables 


### Graphical Descriptive Results for Bream

```{r}
FishiesB=filter(Fishdata, Species =="Bream")
FishiesB=select(FishiesB,-Species)
pairs(FishiesB)
```

In the above Graphical descriptive result chart for "Bream" it appears that 
Length1 and Width would give us the best model regression to test the
prediction.


### Numerical Descriptive Results for Bream

```{r}
summary(FishiesB)
```

In the above summary we have a max. weight of 1000 oz with a max length of 
38 in. using the Length1 variable and a max Height of 18.96 in. and a max
width of 6.8 in.

```{r}
Breammodel2=lm(Weight~Length1+ Width,data=FishiesB)
summary(Breammodel2)
```

In the Bream model 2 above we see an adjr2 of 0.9084.

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = FishiesB,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```


In the above leaps model it appears that the subset size of 2 variables gives us 
a statistical, adjr2 of 0.935.  It indicates that the Length2 and Height are
the best two variables for the models to predict the weight of the "Bream". 
This is the best subset regression for "Bream"




## Inferential Results for Bream

  
```{r}
model.2 <- lm(Weight~Length1+Width,data=FishiesB)
summary.lm(model.2)
```

The inferential chart above appears to have an adjr2 prediction of 0.9084,
using the variables Length1 and width. This is significantly lower than the 
leaps regression model that uses the two variables Length2 and Height with
an adjr2 of 0.935.  It appears that the variables for the bream that best
predict the weight using the leaps subset model is Length2 and Height with
and adjr2 of 0.935. The leaps is the best subset regression model. 

## Build the best regression model you can that predicts the weight of Smelt
## Using only two predictor variables 


### Graphical Descriptive Results for Smelt

```{r}
FishiesS=filter(Fishdata, Species =="Smelt")
FishiesS=select(FishiesS,-Species)
pairs(FishiesS)
```

In the above Graphical descriptive result chart for "Smelt" it appears that 
Length3 and Height would be the best two variables to give us the best model
regression to test the predicted weight for Smelt.



### Numerical Descriptive Results for Smelt

```{r}
summary(FishiesS)
```

In the above summary chart for species "Smelt", it would appear that the
max weight for Smelt is 19.9 oz with a max length of 16.2 in. according to the 
Length3 lm.  and a max Height of 2.9 in. and a max Width of 2.1 in.


```{r}
Smeltmodel3=lm(Weight~Length3 + Height,data=FishiesS)
summary(Smeltmodel3)
```

The model3 above for Smelt appears to have an adjr2 of  0.9307


```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = FishiesS,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```


In the above leaps model it appears that the subset size of 2 variables gives us 
a statistical, adjr2 of 0.9645.  It indicates that the Length2 
and Width are the best two variables for the models to predict the weight of the
"Smelt". This is the best subset regression for "Smelt" 

## Inferential Results for Smelt
  
```{r}
model.3 <- lm(Weight~Length3+Height,data=FishiesS)
summary.lm(model.3)
```

The inferential chart above for Smelt appears to have an adjr2 of 0.9307  
using the two variables Length3 and Height.  

# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variables causes the other, or whether they perhaps are related for some other reason.  Watch the chapter 6 videos from the George Town videos collection.!-->

In conclusion the best regression model appears to be as follows.

# Conclusion 

According to the leaps subset model, the two best variables for the "Perch" are
Height and Width.  This model is the best subset regression for "Perch" with an
adjr2 of 0.9400.

According to the leaps model for "Bream" it appears that the Length2 and Height 
are the best two variables for the models to predict the weight of the "Bream", 
with a statistical, adjr2 of 0.935. This is the best subset regression for
"Bream".


According to the leaps model for "Smelt" it appears that the subset size of 2 
variables Length2 and Width are the best two variables for the best Regression
Model giving us a statistical, adjr2 of 0.9645.  It indicates that the Length2 
and Width are the best two variables for the models to predict the weight of the
"Smelt". This is the best subset regression for "Smelt" 










